Analysis for Non-Expressive performances (ONSET)

### 2020-04-10 material/analysis/stim_n/ioi_duration.Rmd
correct some comments
Signed-off-by: Atsuko Tominaga <Tominaga_Atsuko@phd.ceu.edu>

### Exclude outlier participants
```{r cv_outlier, echo = FALSE}
# for all
cv_all <- cv[, .(N = length(CV), Mean = mean(CV), SD = sd(CV))]
print(cv_all)

>>>>

### Exclude outlier performacnes
```{r cv_outlier, echo = FALSE}
# for all
cv_all <- cv[, .(N = length(CV), Mean = mean(CV), SD = sd(CV))]
print(cv_all)

### 2020-04-10 material/analysis/stim_n/ioi_onset.Rmd
correct some comments
Signed-off-by: Atsuko Tominaga <Tominaga_Atsuko@phd.ceu.edu>

### Exclude outlier participants
```{r cv_outlier, echo = FALSE}
# for all
cv_all <- cv[, .(N = length(CV), Mean = mean(CV), SD = sd(CV))]
print(cv_all)

>>>>

### Exclude outlier performances
```{r cv_outlier, echo = FALSE}
# for all
cv_all <- cv[, .(N = length(CV), Mean = mean(CV), SD = sd(CV))]
print(cv_all)
